sWGS validation report

### 2019-09-04 Validation Report.Rmd
mean norm using cohort values

val.file = '~/Data/BarrettsProgressionRisk/QDNAseq/validation/sWGS_validation_batches.xlsx'
analysis.dir = '~/Data/BarrettsProgressionRisk/Analysis/validation/multipcf'

@@

#all.val %>% filter(!Samplename %in% val$sample )

@@

preds.dir = paste0(analysis.dir, '/predictions/0.9')

>>>>

val.file = '~/Data/BarrettsProgressionRisk/QDNAseq/validation/sWGS_validation_batches.xlsx'
analysis.dir = '~/Data/BarrettsProgressionRisk/Analysis/validation/multipcf'
preds.dir = paste0(analysis.dir, '/predictions/fourier')

@@

@@
